Improving cropland maps through tight integration of human and machine intelligence

### 2019-08-15 manuscript/manuscript.Rmd
Placeholder figure and text for overall map accuracy.

>>>>

## The active learning process
We ran 16 instances to create cropland probability maps for the **X test regions/whole of Ghana**. Each instance covered a distinct mapping geography comprised of one or more adjacent AOIs (Figure 5), ranging in extent from 12,160 to 23,535 km$^2$ (average = 15,457 km$^2$), and represented a separate active learning process. The average number of iterations per active learning process was **X (range = X-X)**, and the average overall accuracy was **X, with a range of X-X** (Figure 5). Overall user's accuracy was slightly **lower/higher** at **X, (range X-X)**, while producer's accuracy averaged **X, (range X-X)**. Each accuracy measure was highest in **northern-northeastern 2/3** of the country, and lowest in **southerwestern 1/3**, where rainfall and cloud-cover are highest, and where tree crops dominate.

<!-- and an accuracy surface interpolated from the average cell-wise accuracies calculated between the predicted map and validation labels.  -->

```{r, echo = FALSE, out.width="80%", fig.cap="The overall, user's, and producer's accuracies (indicated by fill color) for each of the 16 mapping zones (zones numbers are shown on maps) [This a hypothetical placeholder figure].", fig.align='center'}
knitr::include_graphics('figures/figure5.png')
```

## Labelling accuracy
The accuracy patterns generally align with the difficulty of the labelling task, that is, **the southwestern regions were hardest for workers to interpret, as shown by Figure 6.**
